Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-07 longoutput.tex
start rewriting local Hamiltonian reduction

We consider the transform $T\ket{\psi}=\ket{0}\otimes\Re\ket{\psi}+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively. To simplify some notations, let $\ket{\psi}$ be 1-indexed, and let the added qubit be the 0th. Note that after this transformation, the state is real. This transformation preserves measurement results in the standard basis. Under the transform, Hadamard gates are unchanged, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
$$T\circ H_f=H_f\circ T$$
$$T\circ\Lambda_f(P(i)_s)=\Lambda_{f,s}(X_0)\Lambda_{f,s}(Z_0)\circ T=\Lambda_{f,s}(X_0)H_0\Lambda_{f,s}(X_0)H_0\circ T$$

@@

We then attempt to construct a local Hamiltonian with ground state: $$\phi=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
We do so by ensuring states perpendicular to it have high eigenvalues. The basic construction comes from \cite{kitaev2002classical}. The simplification comes from \cite{biamonte_love_2008}.

First, we ensure that the invalid clock states have high eigenvalues.
$$H_{clock}=\sum_{t=1}^{T-1}\ket{01}\bra{01}_{t,t+1}$$
We also set $S_{legal}=\ker H_{clock}$. Note that $S_{legal}$ is precisely the valid clock states; that is, valid unary representations in the time register. Note that $H_{clock}$ can also be written in terms of linear combinations of tensors of $X$, $Z$, and $I$ gates.
$$H_{clock}=\frac{1}{4}((T-1)I + Z_1 - Z_T - \sum_t^{T-1}Z_tZ_{t+1})$$

Then, we ensure that 1-qubit gates are propagated properly. To do so, we set
	$$H_{prop1}=\sum_{t\in T_1}H_{prop,t}$$
	$$H_{prop,t}=I\otimes\ket{\widehat{t}}\bra{\widehat{t}}
		+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
		-U_t\otimes\ket{\widehat{t}}\bra{\widehat{t-1}}
		-U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$

@@

Let $S_{prop1}=\ker H_{prop1}$.
Then, $S_{prop1}$ has the following as basis:
\begin{itemize}
	\item $\ket{00}_{f_t,s_t}\ket{\xi_{00}}\otimes
		(\ket{\widehat{t}}+\ket{\widehat{t+1}}+\ket{\widehat{t+2}})$
	\item $\ket{01}_{f_t,s_t}\ket{\xi_{01}}\otimes
		(\ket{\widehat{t}}+\ket{\widehat{t+1}}-\ket{\widehat{t+2}})$
	\item $\ket{10}_{f_t,s_t}\ket{\xi_{10}}\otimes
		(\ket{\widehat{t}}-\ket{\widehat{t+1}}-\ket{\widehat{t+2}})$
	\item $\ket{11}_{f_t,s_t}\ket{\xi_{11}}\otimes
		(\ket{\widehat{t}}-\ket{\widehat{t+1}}+\ket{\widehat{t+2}})$
\end{itemize}

Also, if $t\in T_2$, that is, $t$ corresponds to a time step where $C_\phi$ is applied, then the following are true due to $C_\phi$ being surrounded by $Z$ gates:
\begin{itemize}
	\item $\ket{0}\bra{0}_{f_t}\otimes
		\ket{\widehat{t}}\bra{\widehat{t}}
		=(\ket{\widehat{t}}+\ket{\widehat{t+1}})
		(\bra{\widehat{t}}+\bra{\widehat{t+1}})$
	\item $\ket{1}\bra{1}_{f_t}\otimes
		\ket{\widehat{t}}\bra{\widehat{t}}
		=(\ket{\widehat{t}}-\ket{\widehat{t+1}})
		(\bra{\widehat{t}}-\bra{\widehat{t+1}})$
	\item $\ket{0}\bra{0}_{s_t}\otimes
		\ket{\widehat{t}}\bra{\widehat{t}}
		=(\ket{\widehat{t+1}}+\ket{\widehat{t+2}})
		(\bra{\widehat{t+1}}+\bra{\widehat{t+2}})$
	\item $\ket{1}\bra{1}_{s_t}\otimes
		\ket{\widehat{t}}\bra{\widehat{t}}
		=(\ket{\widehat{t+1}}-\ket{\widehat{t+2}})
		(\bra{\widehat{t+1}}-\bra{\widehat{t+2}})$
	\item $(\ket{00}\bra{00}_{f_t,s_t}
		+\ket{11}\bra{11}_{f_t,s_t})\otimes
		\ket{\widehat{t}}\bra{\widehat{t}}
		=(\ket{\widehat{t}}+\ket{\widehat{t+2}})
		(\bra{\widehat{t}}+\bra{\widehat{t+2}})$
	\item $(\ket{01}\bra{01}_{f_t,s_t}
		+\ket{10}\bra{10}_{f_t,s_t})\otimes
		\ket{\widehat{t}}\bra{\widehat{t}}
		=(\ket{\widehat{t}}-\ket{\widehat{t+2}})
		(\bra{\widehat{t}}-\bra{\widehat{t+2}})$
\end{itemize}

Similarly,
\begin{itemize}
	\item $\ket{0}\bra{0}_{f_t}\otimes
		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
		=(\ket{\widehat{t-1}}+\ket{\widehat{t-2}})
		(\bra{\widehat{t-1}}+\bra{\widehat{t-2}})$
	\item $\ket{1}\bra{1}_{f_t}\otimes
		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
		=(\ket{\widehat{t-1}}-\ket{\widehat{t-2}})
		(\bra{\widehat{t-1}}-\bra{\widehat{t-2}})$
	\item $\ket{0}\bra{0}_{s_t}\otimes
		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
		=(\ket{\widehat{t-2}}+\ket{\widehat{t-3}})
		(\bra{\widehat{t-2}}+\bra{\widehat{t-3}})$
	\item $\ket{1}\bra{1}_{s_t}\otimes
		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
		=(\ket{\widehat{t-2}}-\ket{\widehat{t-3}})
		(\bra{\widehat{t-2}}-\bra{\widehat{t-3}})$
	\item $(\ket{00}\bra{00}_{f_t,s_t}
		+\ket{11}\bra{11}_{f_t,s_t})\otimes
		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
		=(\ket{\widehat{t-1}}+\ket{\widehat{t-3}})
		(\bra{\widehat{t-1}}+\bra{\widehat{t-3}})$
	\item $(\ket{01}\bra{01}_{f_t,s_t}
		+\ket{10}\bra{10}_{f_t,s_t})\otimes
		\ket{\widehat{t-1}}\bra{\widehat{t-1}}
		=(\ket{\widehat{t-1}}-\ket{\widehat{t-3}})
		(\bra{\widehat{t-1}}-\bra{\widehat{t-3}})$
\end{itemize}

Now we ensure the 1-qubit gates are applied properly. The naive way would be to set
	$$H_t=I\otimes\ket{\widehat t}\bra{\widehat t}
		+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
		-C_\phi\otimes\ket{\widehat t}\bra{\widehat{t-1}}
		-C_\phi^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$
	$$H'=\sum_{t\in T_2}H_t$$
	Equivalently, $H_t=$

	$\ket{00}\bra{00}_{f_t,s_t}\otimes
		(\ket{\widehat{t}}-\ket{\widehat{t-1}})
		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$

	$\ket{01}\bra{01}_{f_t,s_t}\otimes
		(\ket{\widehat{t}}-\ket{\widehat{t-1}})
		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$

	$\ket{10}\bra{10}_{f_t,s_t}\otimes
		(\ket{\widehat{t}}-\ket{\widehat{t-1}})
		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$

	$\ket{11}\bra{11}_{f_t,s_t}\otimes
		(\ket{\widehat{t}}+\ket{\widehat{t-1}})
		(\bra{\widehat{t}}+\bra{\widehat{t-1}})$

However, this cannot be turned into 2-local, so we change the coefficients and set 
	$$H_{prop2}=\sum_{t\in T_2}H_{prop2,t}$$

	$H_{prop2,t}=$

	$\ket{00}\bra{00}_{f_t,s_t}\otimes
		4(\ket{\widehat{t}}-\ket{\widehat{t-1}})
		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$

	$\ket{01}\bra{01}_{f_t,s_t}\otimes
		2(\ket{\widehat{t}}-\ket{\widehat{t-1}})
		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$

	$\ket{10}\bra{10}_{f_t,s_t}\otimes
		2(\ket{\widehat{t}}-\ket{\widehat{t-1}})
		(\bra{\widehat{t}}-\bra{\widehat{t-1}})+$

	$\ket{11}\bra{11}_{f_t,s_t}\otimes
		(\ket{\widehat{t}}+\ket{\widehat{t-1}})
		(\bra{\widehat{t}}+\bra{\widehat{t-1}})$
instead.

Now, if restricted to $S_{prop}$,

	$H_{prop2,t}=H_{qubit,t}+H_{time,t}=$
	$$(-2\ket{0}\bra{0}_{f_t}-2\ket{0}\bra{0}_{s_t}
		+\ket{1}\bra{1}_{f_t}+\ket{1}\bra{1}_{s_t})\otimes$$
	$$(\ket{\widehat{t}}\bra{\widehat{t-1}}+
		\ket{\widehat{t-1}}\bra{\widehat{t}})+$$
	$$(2\ket{0}\bra{0}_{f_t}+2\ket{0}\bra{0}_{s_t}
		+\ket{1}\bra{1}_{f_t}+\ket{1}\bra{1}_{s_t}
		-2\ket{01}\bra{01}_{f_t,s_t}
		-2\ket{10}\bra{10}_{f_t,s_t})\otimes$$
	$$(\ket{\widehat{t-1}}\bra{\widehat{t-1}}+
		\ket{\widehat{t}}\bra{\widehat{t}})$$

Lastly, we check if the input is right...
	$$H_{in}=\sum_{i=m+1}^N\ket{1}\bra{1}_i\otimes\ket{0}\bra{0}$$

Now we use the projection lemma here. This step is different now that $H_{out}$ is gone. I think $J_{in}$ gets dropped or something like that?

>>>>

We consider the transform $T\ket{\psi}=\ket{0}\otimes\Re\ket{\psi}+\ket{1}\otimes\Im\ket{\psi}$, where $\Re$ and $\Im$ denote real and imaginary parts respectively. Note that after this transformation, the state is real. This transformation preserves measurement results in the standard basis. Under the transform, Hadamard gates are unchanged, but controlled phase gates become a combination of Hadamard and Toffoli gates. Mathematically,
$$T\circ H_f=H_f\circ T$$
$$T\circ\Lambda_f(P(i)_s)=\Lambda_{f,s}(X_0)\Lambda_{f,s}(Z_0)\circ T=\Lambda_{f,s}(X_0)H_0\Lambda_{f,s}(X_0)H_0\circ T$$
Where $\ket{\psi}$ is 1-indexed, and the added qubit is in the 0th position.

@@

We then attempt to construct a local Hamiltonian with ground state that encodes the history of the computation: $$\phi=\sum_{t=0}^TU_t...U_1\ket{x}\otimes\ket{\hat{t}}$$
We do so by ensuring states perpendicular to it have high eigenvalues. The base construction comes from \cite{kitaev2002classical}. The simplification is taken from \cite{biamonte_love_2008}.

First, we ensure that the invalid clock states have high eigenvalues by applying the following Hamiltonian to the time register.
$$H_{clock}=\sum_{t=1}^{T-1}\ket{01}\bra{01}_{t,t+1}$$
We also set $S_{legal}=\ker H_{clock}$. Note that $S_{legal}$ is precisely the valid clock states; that is, valid unary representations in the time register. Note that $H_{clock}$ can also be written in terms of linear combinations of tensors of $X$, $Z$, and $I$ gates.
$$H_{clock}=\frac{1}{4}((T-1)I + Z_1 - Z_T - \sum_t^{T-1}Z_tZ_{t+1})$$

Then, we ensure that the initial condition is set up correctly. Let $n$ be the number of the qubits in the circuit.
$$H_{in}=\sum_i^n(I-\ket{x_i}\bra{x_i})\otimes\ket{0}\bra{0}_1$$
Where $x_i$ is the $i$th bit of $x$. The kernel of this is precisely where everything is set up consistently with $\phi$ in time step $t=0$. Furthermore, this can be written in terms of linear combinations of tensors of $X$, $Z$, and $I$ gates as
$$H_{in}=\frac{1}{4}\sum_{i=1}^n(I-(-1)^{x_i}Z_i)\otimes(I+Z_1)$$

TODO define $S_{in}$ when projection lemma is used

Then, we ensure that the gates are applied correctly.
$$H_{prop1}=\sum_{t\in T_1}H_{prop,t}$$
$$H_{prop,t}=I\otimes\ket{\widehat{t}}\bra{\widehat{t}}
	+I\otimes\ket{\widehat{t-1}}\bra{\widehat{t-1}}
	-U_t\otimes\ket{\widehat{t}}\bra{\widehat{t-1}}
	-U_t^\dagger\otimes\ket{\widehat{t-1}}\bra{\widehat{t}}$$

@@
